Pre-screening comments

### 2016-03-06 manuscript.Rmd
set new plot = false for separation plot
add manuscript2.tex and pre-screening-commends

@@

```{r data, warning=FALSE}
library("spduration")
data(bscoup)
bscoup$coup <- ifelse(bscoup$coup == "yes", 1, 0)
bscoup      <- add_duration(bscoup, "coup", unitID = "countryid", tID = "year",
                            freq = "year", ongoing = FALSE)
```

@@

\begin{table}
\begin{center}
\begin{tabular}{lrrrrr} \toprule
Country & Year & Coup & Spell ID & Duration \\ \midrule
Portugal & 1960 & 0 & 1 & 1  \\ 
\ldots & \ldots & 0 & 1 & \ldots \\
\ldots & 1975 & 1 & 1 & 16 \\ \midrule
Portugal & 1976 & 0 & 2 & 1 \\
\ldots & \ldots & 0 & 2 & \ldots \\
\ldots & 2000 & 0 & 2 & 20  \\ \midrule
Canada & 1960 & 0 & 3 & 1 \\
\ldots & \ldots & 0 & 3 & \ldots \\ 
\ldots & 2000 & 0 & 3 & 41 \\ \bottomrule
\end{tabular}
\end{center}
\caption{Example data frame with select duration variables} \label{tab-ex}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
Parameter & Estimate & StdErr & p \\ 
  \hline
(Dur. Intercept) & 2.40 & 0.21 & 0.00 \\ 
  milreg & -1.13 & 0.21 & 0.00 \\ 
  instab & -0.09 & 0.02 & 0.00 \\ 
  regconf & -2.52 & 2.16 & 0.24 \\ 
  log(alpha) & -0.45 & 0.06 & 0.00 \\ 
  (Risk Intercept) & 2.93 & 1.87 & 0.12 \\ 
  couprisk & 0.59 & 0.32 & 0.07 \\ 
  wealth & -0.36 & 0.28 & 0.20 \\ 
  milreg.1 & 10.82 & 9.31 & 0.25 \\ 
  rwar & -0.52 & 0.94 & 0.58 \\ 
  regconf.1 & -5.43 & 5.62 & 0.33 \\ 
  samerica & 2.09 & 1.45 & 0.15 \\ 
  camerica & -0.39 & 0.73 & 0.59 \\ 
   \hline
\end{tabular}
\caption{Coup model with log-logistic hazard} \label{loglog_table}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/sepplots.pdf}
\caption{In-sample separation plots of Weibull and log-logistic model conditional hazard predictions}
\label{insamp}
\end{center}
\end{figure}

@@

par(mfrow = c(2,1),mar = c(2,2,2,2))
separationplot(weib2_test_p,   obs_y)
separationplot(loglog2_test_p, obs_y)
```

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/oos-sepplots.pdf}
\caption{Out-of-sample separation plots}
\label{oos-sepplots}
\end{center}
\end{figure}

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width = 4in]{graphics/rates.pdf}
\caption{Rates of positive outcomes in select publications with binary outcomes}
\label{rates}
\end{figure}

>>>>

```{r}
stop("I've started editing the tex manually")
```

@@

```{r data, warning=FALSE, include=FALSE}
library("spduration")
data(bscoup)
bscoup$coup <- ifelse(bscoup$coup == "yes", 1, 0)
bscoup      <- add_duration(bscoup, "coup", unitID = "countryid", tID = "year",
                            freq = "year", ongoing = FALSE)
```

@@

\begin{table}
\begin{center}
\begin{tabular}{lrrrrr} \toprule
Country & Year & Coup & Spell ID & Duration \\ \midrule
Portugal & 1960 & 0 & 1 & 1  \\ 
\ldots & \ldots & 0 & 1 & \ldots \\
\ldots & 1975 & 1 & 1 & 16 \\ \midrule
Portugal & 1976 & 0 & 2 & 1 \\
\ldots & \ldots & 0 & 2 & \ldots \\
\ldots & 2000 & 0 & 2 & 20  \\ \midrule
Canada & 1960 & 0 & 3 & 1 \\
\ldots & \ldots & 0 & 3 & \ldots \\ 
\ldots & 2000 & 0 & 3 & 41 \\ \bottomrule
\end{tabular}
\end{center}
\caption{Example data frame with select duration variables.} \label{tab-ex}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
Parameter & Estimate & StdErr & p \\ 
  \hline
(Dur. Intercept) & 2.40 & 0.21 & 0.00 \\ 
  milreg & -1.13 & 0.21 & 0.00 \\ 
  instab & -0.09 & 0.02 & 0.00 \\ 
  regconf & -2.52 & 2.16 & 0.24 \\ 
  log(alpha) & -0.45 & 0.06 & 0.00 \\ 
  (Risk Intercept) & 2.93 & 1.87 & 0.12 \\ 
  couprisk & 0.59 & 0.32 & 0.07 \\ 
  wealth & -0.36 & 0.28 & 0.20 \\ 
  milreg.1 & 10.82 & 9.31 & 0.25 \\ 
  rwar & -0.52 & 0.94 & 0.58 \\ 
  regconf.1 & -5.43 & 5.62 & 0.33 \\ 
  samerica & 2.09 & 1.45 & 0.15 \\ 
  camerica & -0.39 & 0.73 & 0.59 \\ 
   \hline
\end{tabular}
\caption{Coup model with log-logistic hazard.} \label{loglog_table}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/sepplots.pdf}
\caption{In-sample separation plots of Weibull and log-logistic model conditional hazard predictions.}
\label{insamp}
\end{center}
\end{figure}

@@

par(mfrow=c(2,1),mar=c(2,2,2,2))
separationplot(weib2_test_p,   obs_y, newplot = FALSE)
separationplot(loglog2_test_p, obs_y, newplot = FALSE)
```

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/oos-sepplots.pdf}
\caption{Out-of-sample separation plots.}
\label{oos-sepplots}
\end{center}
\end{figure}

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width = 4in]{graphics/rates.pdf}
\caption{Rates of positive outcomes in select publications with binary outcomes.}
\label{rates}
\end{figure}
